Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-18 article.tex
wording

We compare our approach to the Pearson correlation, the generalized transfer
entropy (GTE) and GENIE3.

GTE, the baseline of the challenge, measures for all pairs of
neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
$i$ given the observation of the time series of the neuron $j$
conditionally to the observation of past time series of neuron $i$,
whenever the average fluorescence is over a conditioning level.
Conditioning level was set to reproduce baseline of the challenge.

GENIE3 (\cite{huynhthu2010inferring}) translates the inference of the
network of $p$ neurons into $p$ significant variable tasks. For each task,
the fluorescence level of a neuron is predicted from the fluorescence
of all other neurons using a tree based ensemble such as
random forest (\cite{breiman2001random}). The importances
(\cite{louppe2013understanding}) given by the tree ensemble to predict
the time series of a neuron given the others are used to infer
a connectivity score matrix. The following parameters are used
$10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree
node to split the data and the maximal tree depth is constrained
to 1, 2 or 3.

>>>>

We compare our approach to the Pearson correlation (see Section
\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
\begin{description}
\item[GTE], the baseline of the challenge, measures for all pairs of
neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
$i$ given the observation of the time series of the neuron $j$
conditionally to the observation of past time series of neuron $i$,
whenever the average fluorescence is over a conditioning level.
Conditioning level was set to reproduce baseline of the challenge.

\item[GENIE3] (\cite{huynhthu2010inferring}) translates the inference of the
network of $p$ neurons into $p$ supervised learning tasks. For each task,
the fluorescence of a neuron is predicted from the fluorescence
of all other neurons using a tree based ensemble such as
random forest (\cite{breiman2001random}). The tree ensemble associate a
variable importance scores (\cite{louppe2013understanding})
to each neuron used in the predictions.

The following parameters are used
$10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree
node to split the data and the maximal tree depth is constrained
to 1, 2 or 3.
\end{description}
